Reintroduction of disease-resistant individuals allows recovery of an endangered frog in the presence of a lethal fungal disease

### 2022-03-03 doc/manuscript/pnas_demo/pnas_demo.Rmd
Update template to latest Rmarkdown format

---
title: Reintroduction of disease-resistant individuals allows recovery of an endangered frog in the presence of a lethal fungal disease

# Use letters for affiliations, numbers to show equal authorship (if applicable) and to indicate the corresponding author
author:
  - name: Roland A. Knapp
    affiliation: a,b,1
  - name: Thomas C. Smith
    affiliation: a,b
  - name: Mark Q. Wilber
    affiliation: c
  - name: Andrew P. Rothstein
    affiliation: d,e,2
  - name: Allison Q. Byrne
    affiliation: d,e,2
  - name: Maxwell B. Joseph
    affiliation: f

address:
  - code: a
    address: Sierra Nevada Aquatic Research Laboratory, University of California, Mammoth Lakes, CA 93546
  - code: b
    address: Earth Research Institute, University of California-Santa Barbara, Santa Barbara, CA 93106
  - code: c
    address: Department of Forestry, Wildlife, and Fisheries, University of Tennessee, Knoxville, TN, xxxxx
  - code: d
    address: Department of Environmental Science, Policy, and Management, University of California-Berkeley, Berkeley, CA, 94720
  - code: e
    address: Museum of Vertebrate Zoology, University of California-Berkeley, Berkeley, CA, 94720
  - code: f
    address: Earth Lab, University of Colorado, Boulder, CO, 80303

corresponding_author:
  code: 1
  text: "To whom correspondence should be addressed. E-mail: roland.knapp@ucsb.edu"

# For footer text
lead_author_surname: Knapp

## Remove this if not required    
equal_authors:
  code: 2
  text: "A.P.R. and A.Q.B. contributed equally to this work."

author_contributions: |
  R.A.K, T.C.S, M.Q.W, A.P.R., A.Q.B, and M.B.J. designed research; R.A.K, T.C.S, M.Q.W, A.P.R., and A.Q.B performed research; R.A.K, M.Q.W, A.P.R., A.Q.B, and M.B.J. analyzed data; M.B.J. contributed software; and R.A.K, T.C.S, M.Q.W, A.P.R., A.Q.B, and M.B.J. wrote the paper.

## Remove this if not required
conflict_of_interest: |
  The authors declare no conflicts of interest.

abstract: |
  Please provide an abstract of no more than 250 words in a single paragraph. Abstracts should explain to the general reader the major contributions of the article. References in the abstract must be cited in full within the abstract itself and cited in the text.

significance: |
  Authors must submit a 120-word maximum statement about the significance of their research paper written at a level understandable to an undergraduate educated scientist outside their field of speciality. The primary goal of the Significance Statement is to explain the relevance of the work in broad context to a broad readership. The Significance Statement appears in the paper itself and is required for all research papers.

acknowledgements: |
  Please include your acknowledgments here, set in a single paragraph. Please do not include any acknowledgments in the Supporting Information, or anywhere else in the manuscript.

keywords:
  - population recovery
  - amphibian declines
  - emerging infectious disease
  - reintroduction
  - Batrachochytrium dendrobatis

## must be one of: pnasresearcharticle (usual two-column layout), pnasmathematics (one column layout), or pnasinvited (invited submissions only)
pnas_type: pnasresearcharticle

bibliography: pnas.bib
csl: pnas.csl

## change to true to add optional line numbering
lineno: false

output: rticles::pnas_article
---

@@

Results {.unnumbered}
========================================

Evolution of Reduced Disease Susceptibility {#results-subheading1 .unnumbered}
-------------------

Reintroduction of Disease-resistant Frogs {#results-subheading2 .unnumbered}
-------------------

Viability of Reestablished Populations {#results-subheading3 .unnumbered}
-------------------

Conceptual Model of Population Establishment {#results-subheading4 .unnumbered}
-------------------

Discussion {.unnumbered}
========================================

Conclusions {#discussion-subheading1 .unnumbered}
-------------------

Materials and Methods {.unnumbered}
========================================

Statistical Analyses {#methods-subheading1 .unnumbered}
-------------------

Data Availability {#methods-subheading2 .unnumbered}
-------------------

Guide to using this template {.unnumbered}
========================================

@@

Author Affiliations {#author-affiliations .unnumbered}
-------------------

@@

Submitting Manuscripts {#submitting-manuscripts .unnumbered}
----------------------

@@

Format {#format .unnumbered}
------

@@

Manuscript Length {#manuscript-length .unnumbered}
-----------------

@@

References {#references .unnumbered}
----------

References should be cited in numerical order as they appear in text;
this will be done automatically via bibtex, e.g. @belkin2002using and
@berard1994embedding [@coifman2005geometric]. All references, including
for the SI, should be included in the main manuscript file. References
appearing in both sections should not be duplicated. SI references
included in tables should be included with the main reference section.

Data Archival {#data-archival .unnumbered}
-------------

@@

Language-Editing Services {#language-editing-services .unnumbered}
-------------------------

@@

![Placeholder image of a frog with a long example caption to show
justification setting.<span data-label="fig:frog"></span>](frog.png)

Digital Figures {#sec:figures .unnumbered}
---------------

@@

Figure \[fig:frog\] shows an example of how to insert a column-wide
figure. To insert a figure wider than one column, please use the
`\begin{figure*}...\end{figure*}` environment. Figures wider than one
column should be sized to 11.4 cm or 17.8 cm wide.

Single column equations {#single-column-equations .unnumbered}
-----------------------

@@

To allow an equation to span both columns, options are to use the
`\begin{figure*}...\end{figure*}` environment mentioned above for
figures, or to use the `\begin{widetext}...\end{widetext}` environment
as shown in equation \[eqn:example\] below.

@@

<!-- pandoc writes all tables using longtable, which fails in 2-column mode

@@

-->

Supporting Information (SI) {#supporting-information-si .unnumbered}
---------------------------

@@

<!-- Leave these lines as they are at the end of your .Rmd file to ensure placement of methods & acknowledgements sections before the references-->
\showmatmethods
\showacknow
\pnasbreak

>>>>

---
title: Reintroduction of disease-resistant individuals allows recovery of an endangered frog in the presence of a lethal fungal disease
author:
  - name: Roland A. Knapp
    affiliation: a,b,1
  - name: Thomas C. Smith
    affiliation: a,b
  - name: Mark Q. Wilber
    affiliation: c
  - name: Andrew P. Rothstein
    affiliation: d,e,2
  - name: Allison Q. Byrne
    affiliation: d,e,2
  - name: Maxwell B. Joseph
    affiliation: f
address:

  - code: a
    address: Sierra Nevada Aquatic Research Laboratory, University of California, Mammoth Lakes, CA 93546
  - code: b
    address: Earth Research Institute, University of California-Santa Barbara, Santa Barbara, CA 93106
  - code: c
    address: Department of Forestry, Wildlife, and Fisheries, University of Tennessee, Knoxville, TN, xxxxx
  - code: d
    address: Department of Environmental Science, Policy, and Management, University of California-Berkeley, Berkeley, CA, 94720
  - code: e
    address: Museum of Vertebrate Zoology, University of California-Berkeley, Berkeley, CA, 94720
  - code: f
    address: Earth Lab, University of Colorado, Boulder, CO, 80303
corresponding_author:
  code: 1
  text: "To whom correspondence should be addressed. E-mail: roland.knapp@ucsb.edu"
lead_author_surname: Knapp
equal_authors:
  code: 2
  text: "A.P.R. and A.Q.B. contributed equally to this work."
author_contributions: |
  R.A.K, T.C.S, M.Q.W, A.P.R., A.Q.B, and M.B.J. designed research; R.A.K, T.C.S, M.Q.W, A.P.R., and A.Q.B performed research; R.A.K, M.Q.W, A.P.R., A.Q.B, and M.B.J. analyzed data; M.B.J. contributed software; and R.A.K, T.C.S, M.Q.W, A.P.R., A.Q.B, and M.B.J. wrote the paper.   
conflict_of_interest: |
  The authors declare no conflicts of interest.
abstract: |
  Please provide an abstract of no more than 250 words in a single paragraph. Abstracts should explain to the general reader the major contributions of the article. References in the abstract must be cited in full within the abstract itself and cited in the text.
significance: |
  Authors must submit a 120-word maximum statement about the significance of their research paper written at a level understandable to an undergraduate educated scientist outside their field of speciality. The primary goal of the Significance Statement is to explain the relevance of the work in broad context to a broad readership. The Significance Statement appears in the paper itself and is required for all research papers.
acknowledgements: |
  Please include your acknowledgments here, set in a single paragraph. Please do not include any acknowledgments in the Supporting Information, or anywhere else in the manuscript.
keywords:
  - population recovery
  - amphibian declines
  - emerging infectious disease
  - reintroduction
  - Batrachochytrium dendrobatis
## must be one of: pnasresearcharticle (usual two-column layout), pnasmathematics (one column layout), or pnasinvited (invited submissions only)
pnas_type: pnasresearcharticle
bibliography: pnas.bib
csl: pnas.csl
lineno: false
output: rticles::pnas_article
editor_options: 
  markdown: 
    wrap: 72
---

@@

# Results {.unnumbered}

## Evolution of Reduced Disease Susceptibility {#results-subheading1 .unnumbered}

## Reintroduction of Disease-resistant Frogs {#results-subheading2 .unnumbered}

## Viability of Reestablished Populations {#results-subheading3 .unnumbered}

## Conceptual Model of Population Establishment {#results-subheading4 .unnumbered}

# Discussion {.unnumbered}

## Conclusions {#discussion-subheading1 .unnumbered}

# Materials and Methods {.unnumbered}

## Statistical Analyses {#methods-subheading1 .unnumbered}

## Data Availability {#methods-subheading2 .unnumbered}

# Guide to using this template {.unnumbered}

@@

## Author Affiliations {#author-affiliations .unnumbered}

@@

## Submitting Manuscripts {#submitting-manuscripts .unnumbered}

@@

## Format {#format .unnumbered}

@@

## Manuscript Length {#manuscript-length .unnumbered}

@@

## References {#references .unnumbered}

References should be cited in numerical order as they appear in text;
this will be done automatically via bibtex, e.g. @belkin2002using and
[@berard1994embedding; @coifman2005geometric]. All references, including
for the SI, should be included in the main manuscript file. References
appearing in both sections should not be duplicated. SI references
included in tables should be included with the main reference section.

## Data Archival {#data-archival .unnumbered}

@@

## Language-Editing Services {#language-editing-services .unnumbered}

@@

![Placeholder image of a frog with a long example caption to show
justification setting.](frog.png)

## Digital Figures {#sec:figures .unnumbered}

@@

Figure $$fig:frog$$ shows an example of how to insert a column-wide
figure. To insert a figure wider than one column, please use the
`\begin{figure*}...\end{figure*}` environment. Figures wider than one
column should be sized to 11.4 cm or 17.8 cm wide.

## Single column equations {#single-column-equations .unnumbered}

@@

To allow an equation to span both columns, options are to use the
`\begin{figure*}...\end{figure*}` environment mentioned above for
figures, or to use the `\begin{widetext}...\end{widetext}` environment
as shown in equation $$eqn:example$$ below.

@@

```{=html}
<!-- pandoc writes all tables using longtable, which fails in 2-column mode

@@

-->
```
## Supporting Information (SI) {#supporting-information-si .unnumbered}

@@

<!-- Leave these lines as they are at the end of your .Rmd file to ensure placement of methods & acknowledgements sections before the references-->

```{=tex}
\showmatmethods
\showacknow
\pnasbreak
```
